---
title: "CS1"
author: "Akib Hossain"
date: "11/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(tidyverse)
library(GGally)
library(plotly)
library(ggplot2)
library(plyr) # Load first before dplyer 
library(dplyr)
library(tidyr)
library(maps)
library(mapproj)
library(ggalt)
library(class)
library(caret)
library(e1071)
library(tm)
library(mvtnorm)
#library(xlsx)
library(leaflet)
library(ggvis)
```


Testing the text output


# Case study Questions 
## 1. How many breweries are present in each state?
```{r}
beer_csv_loc <- "./Beers.csv"
breweries_csv_loc <- "./Breweries.csv"
# Read in data 
Beer <- read.csv(beer_csv_loc, header = TRUE)
Breweries <- read.csv(breweries_csv_loc, header = TRUE)
#Beer = read.csv(file.choose(),header = TRUE) # read in company data

#Breweries = read.csv(file.choose(),header = TRUE) # read in company data
# Create a seperate data frame to store state data 
### Note: This data set counts the district of columbia as a state
num_of_breweries_by_state <- data.frame(table(Breweries$State))
##### Celia Banks #####
#Begin prepare an interactive geo map of breweries by state
#set the map
leaflet() %>% addTiles()
#add popup for brewery information
brewery_map <- Breweries %>% mutate(popup_info=paste(Name,"<br/>",City,"<br>",State,"<br>"))
#tweak the map with info layout, set circles smaller to enhance visual
#leaflet() %>% addTiles() %>% addCircleMarkers(data=brewery_map, 
 #                                             lat=~Latitude, 
 #                                             lng=~Longitude, 
  #                                            radius=~1, 
  #                                            popup=~popup_info)
#End prepare an interactive geo map of breweries by state#
#corresponding distribution plot of breweries by state
ggplot(brewery_map, aes(x=as.factor(State), color="blue")) +
       geom_bar(color="blue") +
       ggtitle("Distribution of Breweries by State") +
       xlab("State") +
       geom_text(stat='count', aes(label=after_stat(count)), vjust=-.25) +
       theme(legend.position="none", axis.text.x = element_text(angle = 90)) +
       theme(plot.title = element_text(hjust = 0.5))
#corresponding distribution plot of breweries by region
#ggplot(brewery_map, aes(x=as.factor(Region), color="green")) +
#       geom_bar(color="green") +
##       ggtitle("Distribution of Breweries by Region") +
 #      xlab("Region") +
 #      geom_text(stat='count', aes(label=after_stat(count)), vjust=-.25) +
 #      theme(legend.position="none", axis.text.x = element_text(angle = 90)) +
 #      theme(plot.title = element_text(hjust = 0.5))
##### END CB #####
```


## 2. Merge beer data with the breweries data. Print the first 6 observations and
#the last six observations to check the merged file
```{r}
# Change column name of beer_data to match brewery_data to use as a primary key
colnames(Beer)[5] <- "Brew_ID"
# Merge two data bases using merge
full_brew_data <- merge(Breweries, Beer, by="Brew_ID")
# Rename columns 2 and 5 that were changed during the merge
colnames(full_brew_data)[2] <- "Brewery"
colnames(full_brew_data)[5] <- "Beer_Name"
# Print first 6 and last 6 observations 
head(full_brew_data, n=6)
tail(full_brew_data, n=6)


```


## 3. Address any NA values
```{r}
# Create two new tables where one has only ABV with no <NA>'s and the other 
state_abv <- data.frame(State=full_brew_data$State, ABV=full_brew_data$ABV)
state_abv <- state_abv %>% drop_na(ABV)
# Do the same for IBU 
state_ibu <- data.frame(State=full_brew_data$State, IBU=full_brew_data$IBU)
state_ibu <- state_ibu %>% drop_na(IBU)
```


## 4. Compute the median alcohol content and international bitterness unit for each
##state. Plot a bar chart 
```{r, fig.height=7, fig.width=12}
# Find the average ABV for the state_abv table 
avg_state_abv <- ddply(state_abv, .(State), function(x) median(x$ABV))
colnames(avg_state_abv)[2] <- "Median_ABV" # Rename the column
# Drop DC. It's not a state....yet
avg_state_abv <- avg_state_abv[-c(8),] # DC is equal to position 8 on the table 
# Order the states by Decending ABV content 
avg_state_abv <- avg_state_abv[order(avg_state_abv$Median_ABV, decreasing=TRUE),]
# Find Average IBU
avg_state_ibu <- ddply(state_ibu, .(State), function(x) median(x$IBU))
colnames(avg_state_ibu)[2] <- "Median_IBU" # Rename column
# Order the states by IBU Decending 
avg_state_ibu <- avg_state_ibu[order(avg_state_ibu$Median_IBU, decreasing=TRUE),]
# Plot Average Alcohol by Volume per state
ggplot(avg_state_abv, aes(x=reorder(State, desc(Median_ABV)), y=Median_ABV, fill=State)) + 
       geom_col(show.legend = FALSE, width=.9, position="dodge") +
       ggtitle("Median ABV per State") +
       xlab("State") + 
       ylab("Median Alcohol by Volume") 
# Plot Average International Bitterness Unit per State 
ggplot(avg_state_ibu, aes(x=reorder(State, desc(Median_IBU)), y=Median_IBU, fill=State)) + 
       geom_col(show.legend = FALSE, width=.9, position="dodge") +
       ggtitle("Median IBU per State") + 
       xlab("State") + 
       ylab("Median IBU")
```







## 5. Which state has the the Max ABV. Which has the 
```{r}
# Get the State with the highest average ABV
#state_max_abv <- avg_state_abv[which.max(avg_state_abv$Median_ABV),] # KY
state_max_abv <- full_brew_data[which.max(full_brew_data$ABV),] # CO
state_max_abv[c(4,7)]
# Get the State with the highest average IBU
state_max_ibu <- full_brew_data[which.max(full_brew_data$IBU),] # OR
state_max_ibu[c(4,8)]
```
### Kentucky has the highest percentage of alcohal by volume while Maine has the highest IBU. 


## 6. Comment on the Summary stats and distribution of the ABV variable 
```{r}
summary(state_abv)
ggplot(state_abv, aes(x=ABV)) + geom_histogram() # Right Skewness
ggplot(state_abv, aes(x=ABV)) + geom_boxplot()
```


##7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? 
```{r}
# Create a new data frame from the beer data that removes rows that have <NA> in 
# the ABV and IBU columns
beer_data_no_na <- Beer
beer_data_no_na <- beer_data_no_na %>% drop_na(ABV)
beer_data_no_na <- beer_data_no_na %>% drop_na(IBU)
# Scatter plot to show raw data 
ggplot(beer_data_no_na, aes(x=ABV, y=IBU, colour=Style)) + 
       geom_point(show.legend = FALSE) + 
       ggtitle("ABV vs IBU") +
       xlab("ABV in %") + 
       ylab("IBU")
# Plot a smooth curve to see a more "linear" pattern 
ggplot(beer_data_no_na, aes(x=ABV, y=IBU)) + 
       geom_smooth() +
       ggtitle("ABV vs IBU") + 
       xlab("ABV in %") + 
       ylab("IBU")
```


## 8. investigate the difference with respect to IBU and ABV between IPAs (India Pale Ales) 
#and other types of Ale. Use KNN.
```{r, include=FALSE}
# Create a data frame with only IPA's
#df1[grep("dog",df1$type),]
ipa_beers <- beer_data_no_na[grep("IPA",beer_data_no_na$Style),]
# Change the Sytle column to only have the value of IPA for easier model training
ipa_beers$Style <- "IPA"
ales_beer <- beer_data_no_na[grep("Ale",beer_data_no_na$Style),]
# Change the Sytle column to only have the value of Ale for easier model training
ales_beer$Style <- "Ale"
# Combine the two data sets 
ipas_and_ales <- rbind(ipa_beers, ales_beer)
# plot the data to get an initial view of the data
ggplot(ipas_and_ales, aes(x=ABV, y=IBU, colour=Style)) + geom_point()
# Create train and test data frames
ipas_and_ales_train <- ipas_and_ales # train data needs to be a duplicate of orig
ipas_and_ales_test <- data.frame()
# Split 70/30 (Train/Test)
samples_to_take <- round(as.numeric(nrow(ipas_and_ales_train)*.3), digits=0)
for (row in 1:samples_to_take) {
  tmp_row <- sample_n(ipas_and_ales_train, 1) # Take sample
  # Add Sample to test data
  ipas_and_ales_test <- ipas_and_ales_test %>% rbind(tmp_row)
  # Remove Sample from train data
  ipas_and_ales_train <- ipas_and_ales_train[!(ipas_and_ales_train$Beer_ID==tmp_row$Beer_ID),]
}
# find an optimal K value for the KNN model
style_accuracy <- data.frame(accuract=numeric(50), k=numeric(50))
for (iter in 1:50) {
  style_class <- knn(ipas_and_ales_train[,c(3,4)], ipas_and_ales_test[c(3,4)],
                     ipas_and_ales_train$Style,
                     prob=TRUE, k=iter)
  table(ipas_and_ales_test$Style, style_class)
  cm <- confusionMatrix(table(ipas_and_ales_test$Style, style_class))
  style_accuracy$accuracy[iter] <- cm$overall[1]
  style_accuracy$k[iter] <- iter
}
#plot(style_accuracy$k, style_accuracy$accuracy, type="l", xlab="k")
plot_ly(style_accuracy, x=style_accuracy$k, y=style_accuracy$accuracy, 
        type="scatter", mode="lines")
##
## On average this loop gives me an optimal k level of k=5,6,7
##
```